Metric Spaces with Expensive Distances

### 2019-01-24 paper/arxiv_version.tex
Add arxiv version.

\documentclass[a4paper,USenglish]{socg-lipics-v2018}
%\documentclass[a4paper,USenglish]{article}

%\usepackage{arxiv}

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathbbol}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{url}
\usepackage{floatflt}
\usepackage{mathptmx}
\usepackage{epsfig}
\usepackage{wrapfig}
\usepackage{color}

@@

%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{note}[theorem]{Note}

@@

\title{Metric Spaces with Expensive Distances}
\author{Michael Kerber}{TU Graz}{kerber@tugraz.at}{https://orcid.org/0000-0002-8030-9299}{Supported by Austrian Science Fund (FWF) grant number P 29984-N35}
\author{Arnur Nigmetov}{TU Graz}{nigmetov@tugraz.at}{}{}
\authorrunning{M. Kerber and A. Nigmetov}

\keywords{metric spaces, doubling dimension, spanners, approximate nearest neighbor}
%\subjclass{\ccsdesc[500]{Theory of computation~Nearest neighbor algorithms}}
\subjclass{\ccsdesc[500]{Theory of computation~Random search heuristics}}
% \category{dummy}

\Copyright{Michael Kerber and Arnur Nigmetov}

@@

>>>>

%\documentclass[a4paper,USenglish]{socg-lipics-v2018}
\documentclass[a4paper,USenglish]{article}

% uncomment for Arxiv
\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
% END uncomment for Arxiv

\usepackage{booktabs}       % professional-quality tables
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{mathbbol}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{url}
\usepackage{floatflt}
\usepackage{mathptmx}
\usepackage{epsfig}
\usepackage{wrapfig}
\usepackage{color}

@@

% uncomment for Arxiv
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{note}[theorem]{Note}
% END uncomment for Arxiv

@@

\title{Metric Spaces with Expensive Distances}
% uncomment for LIPICS 
%\author{Michael Kerber}{TU Graz}{kerber@tugraz.at}{https://orcid.org/0000-0002-8030-9299}{Supported by Austrian Science Fund (FWF) grant number P 29984-N35}
%\author{Arnur Nigmetov}{TU Graz}{nigmetov@tugraz.at}{}{}
%\authorrunning{M. Kerber and A. Nigmetov}

%\keywords{metric spaces, doubling dimension, spanners, approximate nearest neighbor}
%%\subjclass{\ccsdesc[500]{Theory of computation~Nearest neighbor algorithms}}
%\subjclass{\ccsdesc[500]{Theory of computation~Random search heuristics}}
%% \category{dummy}

%\Copyright{Michael Kerber and Arnur Nigmetov}
% END uncomment for LIPICS

% uncomment for Arxiv
\author{Michael Kerber\\
Graz University of Technology \\
Institut für Geometrie \\
Kopernikusgasse 24, 8010 Graz, Austria \\
\And
Arnur Nigmetov\\
Graz University of Technology \\
Institut für Geometrie \\
Kopernikusgasse 24, 8010 Graz, Austria \\
}
%\\
%kerber@tugraz.at\\
%Supported by Austrian Science Fund (FWF) grant number P 29984-N35
%\And

%Arnur Nigmetov
%Graz University of Technology\\
%Institut fuer Geometrie\\
%Kopernikusgasse 24\\
%8010 Graz\\
%Austria\\
%nigmetov@tugraz.at}

%\keywords{metric spaces, doubling dimension, spanners, approximate nearest neighbor}

% END uncomment for arxiv

@@

% uncomment for Arxiv
\keywords{metric spaces, doubling dimension, spanners, approximate nearest neighbor}
% END uncomment for Arxiv
